Simultaneous Elicitation of Scoring Rule and Agent Preferences for Robust Winner Determination

### 2020-10-05 minimax.tex
More of the plan decided during meeting

1. Pessimistic is feasible and much better than Random
	Graph featuring (5, 10, 150, 200 runs), Random, Pess, L. pess, Elitist.
	And table like table 1.
2. Limited pessimistic performs well.
	Reach regret: $n/10$. For this, we need $m^x n$ questions. TODO Olivier: find $x$. TODO Beatrice: check and compile results in a table specifically for this (see: function regret by k).
	Almost as good as Pess and better than the Elitist one (see previous graphs or table)
	Much faster [do this later]
3. Decrease in MMR is linear with nb of questions
	include nice graph of Beatrice.
4. Value of information qC VS qV with 2 phases and 2phases VS interleaving
	A question to the chair has a similar value (in regret) as a qV.
	Interleaving $k$ questions is similar to asking $p$ questions to the chair first and then $k - p$ to the voters when $p$ is chosen optimally. 
5. Limited pessimistic approx Limited optimistic

>>>>

1. Pessimistic is feasible and much better than Random
	Graph featuring (5, 10, 150, 200 runs), Random, Pess, L. pess, Elitist.
	And table like table 1.
2. Limited pessimistic performs well.
	Reach regret: $n/10$. For this, we need $m^x n$ questions. TODO Olivier: find $x$. TODO Beatrice: check and compile results in a table specifically for this (see: function regret by k).
	Almost as good as Pess and better than the Elitist one (see previous graphs or table)
	Much faster [do this much later]
3. Decrease in MMR is linear with nb of questions
	Redo nice graph of Beatrice with same sizes.
4. Value of information qC VS qV with 2 phases and 2phases VS interleaving
	Interleaving $k$ questions is similar to asking $p$ questions to the chair first and then $k - p$ to the voters when $p$ is chosen optimally. [do this a bit later]
	A question to the chair has a similar value (in regret) as a qV: use the graph summarized by Olivier. Check prop. qC. Check on other sizes.
5. Limited pessimistic approx Limited optimistic [do this much later]
